2016 Brussels Bombings

### 2019-07-13 report/paper.Rmd
Replace dynamic (js) dygraphs with ggplots

---
title: '2016 Brussels Bombings'
subtitle: 'Air Traffic Analysis'
author:
- Ramiro Balado Ordax
- Alejandro Hernández Rubio
- Pol Mesalles Ripoll
output:
    pdf_document:
        highlight: tango
        number_sections: true
        keep_tex: true
always_allow_html: true
---

@@

```{r, fig.align='center'}
ddr.times(data$real$flights, bru, event)
```

@@

```{r, fig.align='center'}
ggplot(data = NULL, aes(y = N.x + N.y)) +
	geom_violin(data = before[orig == bru], aes(x = 'Before')) +
	geom_boxplot(data = before[orig == bru], aes(x = 'Before'), width = 0.1) +
	stat_summary(data = before[orig == bru], aes(x = 'Before'),
				 fun.y = mean, geom = 'point', shape = 5, size = 2.5) +
	geom_violin(data = after[orig == bru], aes(x = 'After')) +
	geom_boxplot(data = after[orig == bru], aes(x = 'After'), width = 0.1) +
	stat_summary(data = after[orig == bru], aes(x = 'After'),
				 fun.y = mean, geom = 'point', shape = 5, size = 2.5) +
	scale_x_discrete(limits = c('Before', 'After')) +
	labs(title = paste('Average Daily Flights at', bru), x = NULL, y = 'Number of Flights') +
	theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r, fig.align='center'}
ddr.map(data$real$routes[id %in% div[, id]], autocenter = FALSE)
```

@@

```{r, fig.align='center'}
dygraph(eu, main = 'European Air Traffic Evolution', ylab = 'Total Number of Flights', width = '100%') %>%
	dyRangeSelector() %>%
	dyLegend(width = '160') %>%
	dyEvent(event[1], 'Airport closes', labelLoc = 'bottom') %>%
	dyEvent(event[2], 'Airport reopens', labelLoc = 'bottom')
```

@@

```{r, fig.align='center'}
ddr.times(data$real$flights, bcn, event)
```

@@

```{r, fig.align='center'}
htmltools::tagList(lapply(nearby, function(airport) {
	ddr.times(data$real$flights, airport, event, group = 'nearby', height = '250px')
}))
```

@@

```{r, fig.align='center'}
ggplot(data = NULL, aes(y = N.x + N.y)) +
	geom_boxplot(data = before[orig %in% nearby], aes(x = orig, color = 'before')) +
	geom_boxplot(data = during[orig %in% nearby], aes(x = orig, color = 'during')) +
	geom_boxplot(data = after[orig %in% nearby], aes(x = orig, color = 'after')) +
	scale_color_manual(limits = c('before', 'during', 'after'), values = c('green', 'red', 'blue'),
					   name = NULL, labels = c('Before the attack', paste('While', bru, 'closed'),
					   						   paste('After', bru, 'reopens'))) +
	scale_x_discrete(limits = nearby) +
	labs(title = 'Average Daily Flights in Nearby Airports', x = NULL, y = 'Number of Flights') +
	theme(plot.title = element_text(hjust = 0.5), legend.position = 'bottom')
```

@@

```{r, fig.align='center'}
htmltools::tagList(lapply(c(bru, nearby), function(icao) {
	dygraph(delays[airport == icao, .(date, depdel, arrdel)],
			main = paste('Average Daily Delays at', icao),
			ylab = paste('Delay (minutes)'),
			group = 'delay',
			width = '100%', height = '250px') %>%
		dySeries('depdel', label = paste('Delay in Departures')) %>%
		dySeries('arrdel', label = paste('Delay in Arrivals')) %>%
		dyRangeSelector() %>%
		dyOptions(colors = c('royalblue', 'coral')) %>%
		dyLegend(width = '350') %>%
		dyEvent(event[1], 'Airport closes', labelLoc = 'bottom') %>%
		dyEvent(event[2], 'Airport reopens', labelLoc = 'bottom')
}))
```

@@

```{r, fig.align='center'}
ggplot(data = NULL, aes(y = depdel)) +
	geom_boxplot(data = delays[date < event[1]], aes(x = airport, color = 'before')) +
	geom_boxplot(data = delays[date >= event[1] & date <= event[2]], aes(x = airport, color = 'during')) +
	geom_boxplot(data = delays[date > event[2]], aes(x = airport, color = 'after')) +
	scale_color_manual(limits = c('before', 'during', 'after'), values = c('green', 'red', 'blue'),
					   name = NULL, labels = c('Before the attack', paste('While', bru, 'closed'),
					   						   paste('After', bru, 'reopens'))) +
	scale_x_discrete(limits = c(bru, nearby)) +
	labs(title = 'Average Daily Departure Delays', x = NULL, y = 'Delay (minutes)') +
	theme(plot.title = element_text(hjust = 0.5), legend.position = 'bottom')
```

```{r, fig.align='center'}
ggplot(data = NULL, aes(y = arrdel)) +
	geom_boxplot(data = delays[date < event[1]], aes(x = airport, color = 'before')) +
	geom_boxplot(data = delays[date >= event[1] & date <= event[2]], aes(x = airport, color = 'during')) +
	geom_boxplot(data = delays[date > event[2]], aes(x = airport, color = 'after')) +
	scale_color_manual(limits = c('before', 'during', 'after'), values = c('green', 'red', 'blue'),
					   name = NULL, labels = c('Before the attack', paste('While', bru, 'closed'),
					   						   paste('After', bru, 'reopens'))) +
	scale_x_discrete(limits = c(bru, nearby)) +
	labs(title = 'Average Daily Arrival Delays', x = NULL, y = 'Delay (minutes)') +
	theme(plot.title = element_text(hjust = 0.5), legend.position = 'bottom')
```

@@

```{r, fig.align='center'}
dygraph(fuckedplot,
		main = 'Most Affected Airlines',
		ylab = 'Number of Flights',
		width = '100%') %>%
	dyRangeSelector() %>%
	dyLegend(width = '360') %>%
	dyEvent(event[1], 'Airport closes', labelLoc = 'bottom') %>%
	dyEvent(event[2], 'Airport reopens', labelLoc = 'bottom')
```

>>>>

---
title: '2016 Brussels Bombings'
subtitle: 'Air Traffic Analysis'
author:
- Ramiro Balado Ordax
- Alejandro Hernández Rubio
- Pol Mesalles Ripoll
output:
    pdf_document:
        highlight: tango
        number_sections: true
        keep_tex: true
header-includes:
- \usepackage{subfig}
always_allow_html: true
---

@@

```{r bru_traffic, fig.align='center', fig.cap=paste('Air Traffic Evolution at', bru)}
ddr.stimes(data$real$flights, bru, event)
```

@@

```{r bru_average, fig.align='center', fig.cap=paste('Average Daily Flights at', bru)}
ggplot(data = NULL, aes(y = N.x + N.y)) +
	geom_violin(data = before[orig == bru], aes(x = 'Before')) +
	geom_boxplot(data = before[orig == bru], aes(x = 'Before'), width = 0.1) +
	stat_summary(data = before[orig == bru], aes(x = 'Before'),
				 fun.y = mean, geom = 'point', shape = 5, size = 2.5) +
	geom_violin(data = after[orig == bru], aes(x = 'After')) +
	geom_boxplot(data = after[orig == bru], aes(x = 'After'), width = 0.1) +
	stat_summary(data = after[orig == bru], aes(x = 'After'),
				 fun.y = mean, geom = 'point', shape = 5, size = 2.5) +
	scale_x_discrete(limits = c('Before', 'After')) +
	labs(x = NULL, y = 'Number of Flights')
```

@@

```{r div_map, fig.align='center', fig.cap=paste('Map of all the diverted flights headed to', bru)}
ddr.map(data$real$routes[id %in% div[, id]], autocenter = FALSE)
```

@@

```{r eu_traffic, fig.align='center', fig.cap='European Air Traffic Evolution'}
ggplot(data = eu) +
	geom_line(aes(x = date, y = N, color = '')) +
	scale_x_date(date_breaks = '1 week', date_labels = '%d/%m') +
	geom_vline(xintercept = event, linetype = 2) +
	labs(x = NULL, y = 'Total Number of Flights', color = NULL) +
	annotate('text', x = event[1], label = 'Airport closes', y = 10, angle = 90, vjust = -1, hjust = 0) +
	annotate('text', x = event[2], label = 'Airport reopens', y = 10, angle = 90, vjust = -1, hjust = 0) +
	theme(legend.position = 'none')
```

@@

```{r bcn_traffic, fig.align='center', fig.cap=paste('Air Traffic Evolution at', bcn)}
ddr.stimes(data$real$flights, bcn, event)
```

@@

```{r nearby_traffic, fig.align='center', fig.cap='Air Traffic Evolution in Nearby Airports', fig.subcap=nearby, fig.ncol=1}
for (airport in nearby) {
	print(ddr.stimes(data$real$flights, airport, event))
}
```

@@

```{r av_flights, fig.align='center', fig.cap='Average Daily Flights in Nearby Airports'}
ggplot(data = NULL, aes(y = N.x + N.y)) +
	geom_boxplot(data = before[orig %in% nearby], aes(x = orig, color = 'before')) +
	geom_boxplot(data = during[orig %in% nearby], aes(x = orig, color = 'during')) +
	geom_boxplot(data = after[orig %in% nearby], aes(x = orig, color = 'after')) +
	scale_color_manual(limits = c('before', 'during', 'after'), values = c('green', 'red', 'blue'),
					   name = NULL, labels = c('Before the attack', paste('While', bru, 'closed'),
					   						   paste('After', bru, 'reopens'))) +
	scale_x_discrete(limits = nearby) +
	labs(x = NULL, y = 'Number of Flights') +
	theme(legend.position = 'top')
```

@@

```{r av_delays, fig.align='center', fig.cap='Average Daily Delays', fig.subcap=nearby, fig.ncol=1}
for (icao in c(bru, nearby)) {
	print(ggplot(data = delays[airport == icao, .(date, depdel, arrdel)], aes(x = date)) +
		geom_line(aes(y = depdel, color = 'Delay in Departures')) +
		geom_line(aes(y = arrdel, color = 'Delay in Arrivals')) +
		scale_x_date(date_breaks = '1 week', date_labels = '%d/%m') +
		geom_vline(xintercept = event, linetype = 2) +
		labs(x = NULL, y = 'Delay (minutes)', color = NULL) +
		annotate('text', x = event[1], label = 'Airport closes', y = 10, angle = 90, vjust = -1, hjust = 0) +
		annotate('text', x = event[2], label = 'Airport reopens', y = 10, angle = 90, vjust = -1, hjust = 0) +
		theme(legend.position = 'top'))
}
```

@@

```{r av_dep, fig.align='center', fig.cap='Average Daily Departure Delays'}
ggplot(data = NULL, aes(y = depdel)) +
	geom_boxplot(data = delays[date < event[1]], aes(x = airport, color = 'before')) +
	geom_boxplot(data = delays[date >= event[1] & date <= event[2]], aes(x = airport, color = 'during')) +
	geom_boxplot(data = delays[date > event[2]], aes(x = airport, color = 'after')) +
	scale_color_manual(limits = c('before', 'during', 'after'), values = c('green', 'red', 'blue'),
					   name = NULL, labels = c('Before the attack', paste('While', bru, 'closed'),
					   						   paste('After', bru, 'reopens'))) +
	scale_x_discrete(limits = c(bru, nearby)) +
	labs(x = NULL, y = 'Delay (minutes)') +
	theme(legend.position = 'top')
```

```{r av_arr, fig.align='center', fig.cap='Average Daily Arrival Delays'}
ggplot(data = NULL, aes(y = arrdel)) +
	geom_boxplot(data = delays[date < event[1]], aes(x = airport, color = 'before')) +
	geom_boxplot(data = delays[date >= event[1] & date <= event[2]], aes(x = airport, color = 'during')) +
	geom_boxplot(data = delays[date > event[2]], aes(x = airport, color = 'after')) +
	scale_color_manual(limits = c('before', 'during', 'after'), values = c('green', 'red', 'blue'),
					   name = NULL, labels = c('Before the attack', paste('While', bru, 'closed'),
					   						   paste('After', bru, 'reopens'))) +
	scale_x_discrete(limits = c(bru, nearby)) +
	labs(x = NULL, y = 'Delay (minutes)') +
	theme(legend.position = 'top')
```

@@

```{r fucked, fig.align='center', fig.cap='Most Affected Airlines'}
	ggplot(data = melt(fuckedplot[, 2:ncol(fuckedplot) := lapply(.SD, as.integer),
								  .SDcols = 2:ncol(fuckedplot)], c('date'))) +
		geom_line(aes(x = date, y = value, color = variable)) +
		scale_x_date(date_breaks = '1 week', date_labels = '%d/%m') +
		geom_vline(xintercept = event, linetype = 2) +
		labs(x = NULL, y = 'Number of Flights', color = NULL) +
		annotate('text', x = event[1], label = 'Airport closes', y = 10, angle = 90, vjust = -1, hjust = 0) +
		annotate('text', x = event[2], label = 'Airport reopens', y = 10, angle = 90, vjust = -1, hjust = 0) +
		theme(legend.position = 'top')
```
